\tool: Revisiting BadUSB with Type-C

### 2021-03-17 WOOT/Files/related_work.tex
comparision JFA

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
from the victim without permission. However, in JFA, this data exfiltration is not
combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
capability.

@@

It is worth noting that our \tool is different from JFA~\cite{JFC}. Juice Filming Attacks cannot control the attacked device, it can only video-capture user inputs during charging. However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.

>>>>

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
from the victim without permission. 
There are two main differences between \tool and JFA: \ding{182} According to the official list of \ac{MHL} Devices~\cite{MHLlist}, the latest device supporting \ac{MHL} is released in 2015, which limits the capabilities of JFA. However, \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range. \ding{183} JFA can only exfiltrate video data under the victim's control of his/her device, while \tool can control the victim's device at the same time as monitoring the screen. For example, when the victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device. However \tool can open the payment application by mouse, exfiltrates the payment QR code, and steal money by scanning the payment QR code.

@@
